
% -----------------------------------------------------------------------------------------------------------------
%\thispagestyle{empty}
%\rule{\linewidth}{2pt}

\begin{thebibliography}{199}
\normalsize\rmfamily

\bibitem{ACJR} M. F. Abad, A. Cordero, J. R. Torregrosa, Fourth-and fifth-order for solving nonlinear systems of equations: An application to the global positioning system, Abstr. Appl. Anal.  2013 (Article ID 586708).

\bibitem{Amat3} S. Amat, S. Busquier, S. Plaza, Review of some iterative root-finding methods from a dynamical point of view,
Sci. Ser. A: Math. Sci. 10 (2004) 3--35.

\bibitem{ABBP} S. Amat, S. Busquier, C. Berm\'udez, S. Plaza,
On two families of high order Newton type methods,
Appl. Math. Letters 25 (2012) 2209--2217.

\bibitem{H-C}  W.F. Ames, Nonlinear Partial Differential Equations in Engineering, Academic press, New York, 1965.

\bibitem{AMXL}   H. An, Z. Mo, X. Xu, X. Liu, On choosing a nonlinear initial iterate for solving the 2-D 3-T heat conduction equations, {J. Comput. Phys.} 228 ({2009})  3268--3287.

\bibitem{ACCT} C. Andreu, N. Cambil, A. Cordero, J.R. Torregrosa, Preliminary Orbit Determination of Artificial Satellites: A Vectorial Sixth-Order Approach, {Abstr. Appl. Anal.} 2013 ({2013}) doi:10.1155/2013/960582.

\bibitem{ACT} V. Arroyo, A. Cordero, J.R. Torregrosa, Approximation of artificial satellites preliminary orbits: The
efficiency challenge. {Math. Comput. Model.} 54 ({2011})  1802--1807.

\bibitem{Aw} F. Awawdeh, On new iterative method for solving systems of nonlinear equations, Numer. Algor.  54 (2010) 395--409.

\bibitem{BCT} D.K.R. Babajee, A. Cordero, J.R. Torregrosa,
Study of iterative methods through the Cayley Quadratic Test,
J. of Comput. and Appl. Math. doi:10.1016/j.cam.2014.09.020.

\bibitem{Bateman} H. Bateman, Some recent researches in motion of fluids, Mon. Weather Rev. 43 (1915) 163--170.

\bibitem{blanchard2} P. Blanchard,
Complex Analytic Dynamics on the Riemann Sphere,
Bull. of the AMS 11(1) (1984) 85--141.

\bibitem{blanchard}  P. Blanchard,
The Dynamics of Newton's Method,
Proc. of Symp. in Appl. Math.  49 (1994) 139--154.

\bibitem{boyd} J.P. Boyd, One-point pseudospectral collocation for the one-dimensional Bratu equation, Appl. Math. Comput. 217 (2011) 5553--5565.

\bibitem{bratu}  G. Bratu, Sur les equation integrals non-lineaires, Bull. Math. Soc. France 42 (1914) 113--142.

\bibitem{BB}   D.D. Bruns, J.E. Bailey, Nonlinear feedback control for operating a nonisothermal CSTR near an unstable steady state, {Chem. Eng. Sci.} 32 ({1977})  257--264.

\bibitem{buckmire} R. Buckmire, Applications of Mickens finite differences to several related boundary value problems, in: R.E. Mickens (Ed.), Advances in the Applications of Nonstandard Finite Difference Schemes, World Scientific Publishing, Singapore, 2005, 47--87.

\bibitem{Burgers} J.M. Burgers, A mathematical model illustrating the theory of turbulence, Advances in Applied Mechanics 1 (1948) 171--199.

\bibitem{CCT} F. Chicharro, A. Cordero, J.R. Torregrosa,
Drawing dynamical and parameter planes of iterative families and
methods, The Sci. World J. 2013 (2013) Article ID 780153.

\bibitem{CT}    A. Cordero, J.R. Torregrosa, Variants of Newton's method using fifth-order quadrature formulas, Applied Mathematics and Computation  190 (2007) 686--698.

\bibitem{CHMT} A. Cordero, J.L. Hueso, E. Mart\'{\i}nez, J.R. Torregrosa, A modified Newton-Jarratt's composition, Numer. Algor. 55 (2010) 87--99.

\bibitem{CGTVV} A. Cordero, J. Garc\'{\i}a-Maim\'{o}, J.R. Torregrosa, M.P. Vassileva and P. Vindel,
Chaos in King's iterative family, Appl. Math. Lett. 26 (2013) 842--848.

\bibitem{CTV} A. Cordero, J.R. Torregrosa and P. Vindel,
Dynamics of a family of Chebyshev-Halley type method,
Appl. Math. and Comput. 219 (2013) 8568--8583.

\bibitem{napoles} A. Cordero, L. Feng, A. Franques and J.R. Torregrosa, Stability of a Fourth-Order Family of Iterative Methods for Solving Nonlinear
Problems, 9th International Conference on Engineering Computational
Technology, ISBN 978-1-905088-60-7.

\bibitem{paperburgers} A. Cordero, A. Franques and J.R. Torregrosa, Numerical Solution of Turbulence Problems by Solving
Burgers’ Equation, Algorithms 8 (2015) 224--233, doi:10.3390/a8020224

\bibitem{paperhomeiersistemas} A. Cordero, A. Franques and J.R. Torregrosa, Multidimensional Homeier's generalized class and its
application to planar 1D Bratu problem, SeMA Journal, doi:10.1007/s40324-015-0037-x

\bibitem{devaney} R.L. Devaney, The Mandelbrot Set, the Farey Tree and the Fibonacci sequence, Am. Math. Monthly 106 (4) (1999) 289--302.

\bibitem{EG}   J.A. Ezquerro, J.M. Guti\'errez, M.A. Hern\'{a}ndez, M.A. Salanova, Chebyshev-like methods and quadratic equations, {Rev. Anal. Num\'er.  Th\'eor. Approx.} 28 ({1999}) 23--35.

\bibitem{bratu2} I.M. Gelfand, Some problems in the theory of quasi-linear equations, Trans. Amer. Math. Soc. Ser. 2 (1963) 295--381.

\bibitem{GHR} J.M. Guti\'errez, M.A. Hern\'andez and N. Romero,
Dynamics of a new family of iterative processes for quadratic polynomials,
J. of Comput. and Appl. Math.  233 (2010) 2688--2695.

\bibitem{HSH}  I.A. Hassanien, A.A. Salama, H.A. Hosham, Fourth-order finite difference method for solving Burgers' equation,
{Appl. Math. Comput.} 170 ({2005}) 781--800.

\bibitem{Ho} H.H.H. Homeier, On Newton-type methods with cubic convergence, J. Comput. Appl. Math. 176 (2005) 425--432.

\bibitem{bratu4} J. Jacobsen, K. Schmitt, The Liouville-Bratu-Gelfand problem for radial operators, J. Differential Equations 184 (2002) 283--298.

\bibitem{bratu5} R. Jalilian, Non-polynomial spline method for solving Bratu's problem, Comput. Phys. Comm. 181 (2010) 1868--1872.

\bibitem{Jarratt}  P. Jarratt, Some fourth order multipoint iterative methods for solving equations, Math. Comp. 20 (1966) 434--437.

\bibitem{KA}   M.K. Kadalbajoo, A. Awasthi,
A numerical method based on Crank-Nicolson scheme for Burgers' equation,   {Appl. Math. Comput.} 182 ({2006}) 1430--1442.

\bibitem{KKB} V. Kanwar, S. Kumar, R. Behl, Several New Families of Jarratt's Method for Solving Systems of Nonlinear Equations,
Applications and Appl. Math. 8(2) (2013) 701--716.

\bibitem{KT} H.T. Kung, J.F. Traub, Optimal order of one-point and multipoint
iteration, J. Assoc. Comput. Math. 21 (1974) 634--651.

\bibitem{Lowrie}  R.B. Lowrie, A comparison of implicit time integration methods for nonlinear relaxation and diffusion, {J. Comput. Phys.} 196 {(2004)} 566--590.

\bibitem{Ma} \'A. A. Magre\~{n}\'an, Different anomalies in a Jarrat family of iterative root-finding methods, App. Math. Comput. 233 (2014) 29--38.

\bibitem{MS} R.C. Mittal,  P. Singhal, Numerical solution of Burger's equation. {Commun. Numer. Methods Eng.} 9 ({1993}) 397--406.

\bibitem{mohsen} A. Mohsen, A simple solution of the Bratu problem, Comput. Math. with Appl. 67 (2014) 26--33.

\bibitem{NCS} B. Neta, C. Chun, M. Scott, Basins of attraction for optimal eighth order methods to find simple roots of nonlinear equation, App. Math. Comput. 227 (2014) 567--592.

\bibitem{ostrowski} A.M. Ostrowski, Solutions of equations and systems of equations, Academic Press, New York-London, 1966.

\bibitem{PB} M. Petkovi\'{c}, B. Neta, L. Petkovi\'{c}, J. D\v zuni\'{c}, Multipoint Methods for Solving Nonlinear Equations, Academic Press, Amsterdam, 2013.

\bibitem{SNC} M. Scott, B. Neta, C. Chun,
Basin attractors for various methods,
Appl. Math. and Comput. 218 (2011)
2584--2599.

\bibitem{SA} J.R. Sharma, H. Arora, On efficient weighted-Newton methods for solving systems of nonlinear equations, Appl. Math. Comput. 222 (2013) 497--506.

\bibitem{SGS} J. R. Sharma, R. K. Guna, R. Sharma, An efficient fourth order weighted-Newton method for systems of nonlinear equations, Numer. Algor. 62 (2013) 307--323.

\bibitem{TR}  J.F. Traub, {Iterative Methods for the Solution of Equations}, Chelsea Publishing Company: New~York, NY, USA, 1982.

\bibitem{Va} J.L. Varona, Graphic and numerical comparison between iterative methods, Math. Intelligencer 24 (2002) 37--46.

\bibitem{bratu3} Y.Q. Wan, Q. Guo, N. Pan, Thermo-electro-hydrodynamic model for electrospinning process, Int. J. Nonlinear Sci. Numer. Simul. 5 (2004) 5--8.

\bibitem{WT}   S.S. Wani, S.H. Thakar, Crank-Nicolson type method for Burgers' equation,    {Int. J. Appl. Phys. Math.} 3 ({2013}) 324--328.

\bibitem{weerakoon} S. Weerakoon, T.G.I. Fernando, A variant of Newton’s method with accelerated third-order convergence, Appl. Math. Lett. 13 (2000) 87--93

\bibitem{WPK}   J. Willert, H. Park, D.A. Knoll, A comparison of acceleration methods for solving the neutron transport k-eigenvalue problem, {J. Comput. Phys.} 274 ({2014}) 681--694.
\end{thebibliography}